Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 content/example.tex
minor changes

In summary, the example discussed in this section shows how the precision of 
IFDS-based taint analysis can be improved by taking into account how paths
become infeasible in the presence of correlated calls. In particular, we have
shown how a false positive reported by a standard IFDS-based algorithm is eliminated.
While the discussion in this section has focused on the specific problem of taint analysis,
we would like to emphasize that our technique generally applies to \textit{any}
dataflow analysis problem that can be expressed in the IFDS framework. This includes
many common analysis tasks such as \TODO{please add a few examples + citations}

\subsection{Occurrences of Correlated Calls}
How often do correlated calls occur in practice? To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occurred programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat}.

@@

We can see that on average, 3\% of all call sites $C$ are polymorphic call sites $C_P$.
\mtodo{Should we explain in a footnote why the number of polymorphic call sites is so low?}
Out of those call sites, 38\% are correlated call sites $C^\Subset$. We also see that for one correlated-call receiver, there are on average three correlated calls.

>>>>

In summary, the example discussed in this section shows how the precision of 
IFDS-based taint analysis can be improved by taking into account how paths
become infeasible in the presence of correlated calls. In particular, we have
shown how a false positive reported by a standard IFDS-based algorithm is eliminated.
While the discussion in this section has focused on the specific problem of taint analysis,
we would like to emphasize that our technique generally applies to \textit{any}
dataflow analysis problem that can be expressed in the IFDS framework. This includes
many common analysis tasks such as reaching definitions, constant propagation, etc.
\ftodo{Ondrej, can you give a few more/better examples?}

\subsection{Occurrences of Correlated Calls}
How often do correlated calls occur in practice? To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat}.

@@

In these programs, on average, only 3\% of all call sites $C$ are polymorphic call sites $C_P$.
\mtodo{Should we explain in a footnote why the number of polymorphic call sites is so low?}
However, it is worth noting that out of those call sites, a significant fraction (38\%) are correlated 
call sites $C^\Subset$. We also see that, on average,  each correlated-call receiver is involved in three correlated calls.
